Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-08-30 talk/talk.tex
Describe the two CP approaches

\begin{frame}{Connectedness as a Constraint}
\end{frame}

\begin{frame}{Connectedness via Restricted Branching}
\end{frame}

>>>>

\begin{frame}{Connectedness as a Constraint}
    \begin{itemize}
        \item Once we have assigned one variable to a non-$\bot$ value, traverse the variable graph,
            ignoring any variables assigned to $\bot$. Assign any unvisited variables to $\bot$.
        \item Repeat whenever any variable is assigned to $\bot$ during search.
        \item Also, traverse the value graph, ignoring any values not present in any domain. Remove
            any unvisited values from every domain.
        \item Repeat whenever a value is removed from every domain during search.
    \end{itemize}
\end{frame}

\begin{frame}{Connectedness via Restricted Branching}
    \begin{itemize}
        \item When selecting a variable for branching (except for the first variable), only select
            from variables which are adjacent to at least one variable already assigned to
            non-$\bot$.
        \item If no such variable exists, assign every remaining domain to $\bot$.
    \end{itemize}
\end{frame}
